openarchaeoCollaboration

### 2021-06-14 analysis/paper.Rmd
Enhance platforms plot
Now broken down by first author

```{r plot-categories}
oarch %>%
  group_by(category) %>%
  drop_na(category) %>%
  summarise(n = n()) %>%
  ggplot(aes(fct_reorder(category, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Categories",
    caption = "Data: open-archaeo.info",
    x = NULL, y = "Number of projects"
  )
```

```{r plot-platforms}
oarch %>%
  group_by(platform) %>%
  drop_na(platform) %>%
  summarise(n = n()) %>%
  ggplot(aes(fct_reorder(platform, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Repository platforms",
    caption = "Data: open-archaeo.info",
    x = NULL, y = "Number of projects"
  )
```

@@

ZB: Break down platform by contributors, since a few people may be prolific in their support of a platform without necessarily representing the whole population.

>>>>

```{r plot-categories}
oarch %>%
  drop_na(category) %>%
  group_by(category) %>%
  summarise(n = n()) %>%
  ggplot(aes(fct_reorder(category, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Most popular categories",
    subtitle = "By number of projects",
    caption = "Data: open-archaeo.info",
    x = NULL, y = NULL
  )
```

```{r plot-platforms}
oarch %>%
  drop_na(platform) %>%
  group_by(platform, author1_name) %>%
  summarise(n = n(), .groups = "drop_last") %>%
  mutate(total = sum(n)) %>% 
  ggplot(aes(fct_reorder(platform, total), n, group = author1_name)) +
  geom_col(colour = "white") +
  coord_flip() +
  labs(
    title = "Most popular platforms",
    subtitle = "By number of projects, grouped by primary author",
    caption = "Data: open-archaeo.info",
    x = NULL, y = NULL
  )
```

@@
